---
title: "The Good, the Bad, and the Ugly"
output: github_document
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = T, warning = F, message = F, error = F)
```


This repo stores code and graphics from my thesis project which investigates the use of sentiment in parliamentary speeches. 
For this purpose I parsed German Parliamentary speeches between 1989 and 2018. The core results have been tested with the 
ParlSpeech Corpus in a multilingual comparison. 


## Packages 

```{r}
pacman::p_load(tidyverse, purrr, lubridate, visdat, glue, ggpubr, janitor, tidyr, arm, stargazer, broom, ggthemes, stringr, forcats)

theme_set(theme_classic2())

add_election <- function(x){
  x %>%
    split(.$party) %>%
    map(~{
      .x %>% 
      unique %>%
      geom_rect(
        data = ., 
        aes(xmin = year, xmax = dplyr::lead(year), ymin = -Inf, ymax = Inf, fill = factor(gov)), 
        color = NA, alpha = .1
      )
    })
}

party_colors  <- c("SPD" = "#E2001A", 
                   "CDU/CSU" = "black", #"#e95d0f", 
                   "GRUENE" = "#46962b", 
                   "PDS/LINKE" = "#8B1A1A", 
                   "FDP" = "#ffed00",
                   "AfD" = "#00BFFF")
```


# German Bundestag Speeches

This is the regex to extract features like party_leader (group) for each legislative period. 

```{r}
party_leader19 <- c(
  "Alexander Gauland", "Alice Weidel",
  "Volker Kauder", 
  "Andrea Nahles",
  "Christian Lindner",
  "Anton Hofreiter", "Katrin Göring-Eckardt",
  "Dietmar Bartsch", "Sahra Wagenknecht"
) %>% paste(collapse = "|")

party_leader18 <- c(
  "Volker Kauder", 
  "Thomas Oppermann",
  "Anton Hofreiter", "Katrin Göring-Eckardt",
  "Dietmar Bartsch", "Sahra Wagenknecht"
) %>% paste(collapse = "|")

party_leader17 <- c(
  "Volker Kauder", 
  "Frank-Walter Steinmeier",
  "Rainer Brüderle",
  "Renate Künast", "Jürgen Trittin",
  "Gregor Gysi"
) %>% paste(collapse = "|")

party_leader16 <- c(
  "Volker Kauder", 
  "Peter Struck",
  "Birgit Homburger", "Guido Westerwelle",
  "Renate Künast", "Fritz Kuhn",
  "Gregor Gysi", "Oskar Lafontaine"
) %>% paste(collapse = "|")

party_leader15 <- c(
  "Angela Merkel",
  "Volker Kauder", 
  "Franz Müntefering",
  "Wolfgang Gerhardt",
  "Krista Sager", "Katrin Göring-Eckardt"
) %>% paste(collapse = "|")


party_leader14 <- c(
  "Wolfgang Schäuble",
  "Peter Struck", "Ludwig Stiegler",
  "Wolfgang Gerhardt",
  "Kerstin Müller", "Rezzo Schlauch",
  "Gregor Gysi"
) %>% paste(collapse = "|")

party_leader13 <- c(
  "Wolfgang Schäuble",
  "Rudolf Scharping",
  "Hermann Otto Solms",
  "Joschka Fischer", "Kerstin Müller"
) %>% paste(collapse = "|")

chairs <- c("Bundestagspr.sident", "Bundestagspräsidentin", "Alterspräsident", "Alterspräsidentin", "Bundespräsindet", "Präsidentin", "Präsident")
```


The Bundestag speeches have been parsed before hand and can be downloaded [HERE](https://mega.nz/#!FxljHKSI!a6v21YAb0U6YS93YRJaS0oilSSB3ppUEtNT8ihPXzFk). Sentiment predictions, as well as topic assignments have been already attached. If you are interest in how these got computed, please refer to the multiligual part, where the prediction process is illustrated. The model and tokenizer is included fpr reproducability. Please also see the session info for package versions at the end of the document. 

```{r}
load("data/plenary_final.Rdata")

ps <- plenary_final %>% 
  mutate(sentz = scale(sent)[, 1]) %>%
  #filter(party != "none") %>%
  drop_na(speaker) %>%
  mutate(gov = ifelse(gov == 1, "Gov", "Opp") %>% factor(., levels = c("Opp", "Gov"))) %>% 
  mutate(
    week = lubridate::week(cdate), 
    year = lubridate::year(cdate),
    date_index = glue::glue("{year}_{week}")
  ) %>% 
  group_by(period) %>% 
  arrange(desc(cdate)) %>% 
  mutate(
    until_elect = cdate %>% as.factor %>% as.numeric,
    until_elect_week = date_index %>% as.factor %>% as.numeric
  ) %>% 
  ungroup %>% 
  mutate(chair = ifelse(role %in% chairs, 1, 0)) %>% 
  mutate(minister = ifelse(is.na(party) & !role %in% chairs, 1, 0)) %>% 
  mutate(
    party_leader = case_when(
      period == 19 & str_detect(speaker, party_leader19) ~ 1,
      period == 18 & str_detect(speaker, party_leader18) ~ 1,
      period == 17 & str_detect(speaker, party_leader17) ~ 1,
      period == 16 & str_detect(speaker, party_leader16) ~ 1,
      period == 15 & str_detect(speaker, party_leader15) ~ 1,
      period == 14 & str_detect(speaker, party_leader14) ~ 1,
      period == 13 & str_detect(speaker, party_leader13) ~ 1,
      T ~ 0
    )
  ) %>% 
  mutate(nword100 = (nword/100)) %>% 
  mutate(dr = ifelse(is.na(salutation), 0, 1)) %>%
  mutate(mwordlen = scale(mwordlen)[,1], nword100 = scale(nword)[, 1]) %>% 
  mutate(afd = ifelse(party == "AfD", 1, 0))

glimpse(ps)
```

Get an understanding of the missingness in the data.

```{r}
plenary_final %>% 
  filter(period == 19) %>%
  vis_miss()
```


Mean/Median of government and opposition members and a speaker-wise
comparison of PMs who switch to government status (at least once). 


```{r}
party_box <- ps %>%
  group_by(cdate, party, gov) %>%
  summarise(sentz = mean(sentz)) %>%
  ungroup %>%
  ggplot(aes(gov, sentz, colour = gov)) +
  #geom_histogram(color = NA, alpha = .5) +
  geom_boxplot(alpha = .3) +
  geom_jitter(alpha = .02) +
  theme_classic() +
  scale_colour_manual("", values = c("red", "blue")) +
  labs(x = "", y = "Standardized Sentiment") + 
  stat_compare_means(method = "t.test", comparisons = list(c("Gov", "Opp")))

speaker_compare <- ps %>%
  group_by(speaker, party, gov) %>%
  summarise(sentz = mean(sentz), n = n()) %>%
  ungroup %>% 
  filter(n > 5) %>% 
  arrange(speaker) %>% 
  group_by(speaker) %>% 
  mutate(n_speaker = n()) %>%
  ungroup %>% 
  filter(n_speaker > 1) 

gg_speaker <- speaker_compare %>% 
  #filter(sentz > -1.5) %>% 
  filter(party %in% c("CDU/CSU", "SPD", "DIE GRÜNEN", "FDP")) %>% 
  mutate(party = factor(party, levels = c("CDU/CSU", "SPD", "DIE GRÜNEN", "FDP"))) %>% 
  ggplot(aes(gov, sentz, fill = gov)) +
  geom_violin(alpha = .4, color = NA) +
  geom_line(aes(group = speaker), alpha = .1, color = "gray50") +
  labs(x = "", y = "Standardized Sentiment") + 
  scale_fill_manual("", values = c("red", "blue")) 

ggpubr::ggarrange(party_box, gg_speaker, ncol=2, nrow=1, common.legend = TRUE, legend="none", labels = c("A", "B"))
```


```{r, fig.width = 10, fig.height= 8}
# devtools::install_github("yutannihilation/gghighlight")
vlines <- tibble(
  cdate = c("2013-12-17", "2009-10-28", "2005-11-22", "1998-10-27") %>%  as.Date
)

gg_sent_party <- ps %>% 
  mutate(party = factor(party, levels = c("CDU/CSU", "SPD",  "FDP", "DIE GRÜNEN", "AfD", "DIE LINKE"))) %>% 
  group_by(year, month, party, gov) %>% 
  summarise(msent = mean(sentz), cdate = cdate[1]) %>% 
  ungroup %>% 
  ggplot(aes(cdate, msent, colour = gov)) +
  geom_point(alpha = .4) +
  gghighlight::gghighlight(use_direct_label = F) +
  facet_wrap(~party, ncol = 2) +
  geom_smooth(aes(group = party), color = "gray50", alpha = .3) +
  xlim(as.Date("1986-01-01"), as.Date("2018-08-01")) +
  scale_colour_manual(values = c("blue", "red"))  +
  ylim(-1, 1) +
  theme_classic() +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 30)) +
  geom_vline(data = vlines, aes(xintercept = cdate), linetype = "dashed") 

gg_sent_party
```



## Modeling Sentiment

```{r, results='asis'}
fit_sent_gov_ols1 <- ps %>% 
  lm(sentz ~ gov, data = .)

fit_sent_gov_ols2 <- ps %>% 
  lm(sentz ~ gov + party_leader + minister + chair, data = .)

fit_sent_gov_ols3 <- ps %>% 
  lm(sentz ~ gov + party_leader + minister + chair + until_elect_week + year + mwordlen + log(nword), data = .)

fit_sent_gov_ols4 <- ps %>%
  lm(sentz ~ gov + party_leader + minister + chair + until_elect_week + year + mwordlen + log(nword) + gender + afd, data = .)



fit_sent_gov_ml1 <- ps %>% 
  lmer(sentz ~ gov + (1|party), data = .)

fit_sent_gov_ml2 <- ps %>% 
  lmer(sentz ~ gov + party_leader + minister + chair + (1|party), data = .)

fit_sent_gov_ml3 <- ps %>% 
  lmer(sentz ~ gov + party_leader + minister + chair + until_elect_week + year + mwordlen + log(nword) + (1|party), data = .)

fit_sent_gov_ml4 <- ps %>% 
  lmer(sentz ~ gov + party_leader + minister + chair + until_elect_week + year + mwordlen + log(nword) + gender + afd + (1|party), data = .)

stargazer::stargazer(
  list(
    fit_sent_gov_ols2, 
    fit_sent_gov_ols3, 
    fit_sent_gov_ols4,
    fit_sent_gov_ml2, 
    fit_sent_gov_ml3,
    fit_sent_gov_ml4
  ), 
  type = "html", 
  header = F, title = "Modeling Government vs Opposition Sentiment", font.size = "scriptsize", style = "ajps"
  #out = "coef_table.tex"
)
```


Point Estimates and Confidence Intervals (95%) for each model and term


```{r}
params <- list(
    #fit_sent_gov_ols2, 
    fit_sent_gov_ols3, 
    fit_sent_gov_ols4,
    #fit_sent_gov_ml2, 
    fit_sent_gov_ml3,
    fit_sent_gov_ml4
  ) %>% 
  map2(.y = 1:length(.),~{
    tidy(.x) %>% 
      mutate(model = paste0(.y)) 
  }) %>% 
  bind_rows()

pd <- position_dodge(width = 1.5)
params %>% 
  mutate(color = ifelse(estimate > 0, "1", "0")) %>% 
  mutate(term = forcats::fct_reorder(term, estimate)) %>% 
  filter(!term %in% c("(Intercept)", "sd_Observation.Residual", "sd_(Intercept).party")) %>% 
  ggplot(aes(term, estimate, colour = color, shape = model)) +
  geom_point(position = pd) +
  geom_linerange(
    aes(
      ymin = estimate - 1.96*std.error, 
      ymax = estimate + 1.96*std.error),
    position = pd
  ) +
  coord_flip() +
  geom_violin(color = "black") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray70") +
  guides(colour = F) +
  scale_colour_manual(values = c("red", "blue"))
```

```{r}
rs_nword <- ps %>%
  filter(period == 19) %>% 
  drop_na(party) %>% 
  filter(party != "none") %>% 
  ggplot(aes(log(nword), sentz, colour = party)) +
  geom_smooth(method = "lm") +
  scale_colour_manual(values = party_colors) +
  theme_classic() +
  labs(x = "Log Number of Words", y = "Standardized Sentiment") +
  theme(legend.position = "none")

rs_mwordlen <- ps %>%
  filter(period == 19) %>% 
  drop_na(party) %>% 
  filter(party != "none") %>% 
  ggplot(aes(mwordlen, sentz, colour = party)) +
  geom_smooth(method = "lm") +
  scale_colour_manual("", values = party_colors) +
  theme_classic() +
  labs(x = "Mean Word Length (mwordlen)", y = "Standardized Sentiment") +
  theme(legend.position = "none") +
  xlim(-2.5, 2.5)

library(ggpubr)
ggarrange(rs_nword, rs_mwordlen, ncol=2, nrow=1, common.legend = TRUE, legend="bottom", labels = c("A", "B"))
```





# Multiligual Sentiment

Download original parlspeech data from [HERE](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/E4RSP9) and place them into the data/parlspeech folder.


```{r}
parl_corpora <- dir("data/parlspeech") %>% 
  purrr::keep(~str_detect(.x, "Corp")) %>% 
  #purrr::map(~get(load(.x))) %>%
  furrr::future_map(~get(load(glue::glue("data/parlspeech/{.x}")))) %>% 
  map_df(~.x %>% mutate_at(vars(session, speechnumber), as.character)) %>% 
  mutate(
    nwords = str_count(text, "\\W+"),
    nchars = nchar(text)
  ) %>%
  mutate(id = glue::glue("{parliament}_{session}_{speechnumber}"))

glimpse(parl_corpora)
```


```{r}
parl_corpora %>% 
  filter(nwords > 195 & nwords < 205) %>%
  .$nchars %>% hist  

parl_corpora %>% 
  filter(nchars > 495 & nchars < 505) %>%
  .$nwords %>% hist  
```


## Predict Sentiment

```{r, eval = F}
library(keras)
options(scipen = 999)

model <- keras::load_model_hdf5("models/cnn_gru_model_86_mac")
char_tokenizer <- keras::load_text_tokenizer("models/char_tokenizer_86_mac")
maxlen <- 500

glimpse(parl_corpora)

parl_preds <- parl_corpora %>%
  dplyr::select(id, text) %>%
  mutate(seq = 1:n() %/% 50000) %>%
  split(.$seq) %>%
  map_df(~{
    print(.x$seq[1])
    parl_char_seq <- char_tokenizer %>% 
      texts_to_sequences(.x$text) %>% 
      pad_sequences(maxlen = maxlen, value = 0)
    
    preds <- predict(model, x = parl_char_seq) %>%
      as_tibble() %>% 
      round(3) %>% 
      set_names(c("sent", "de", "es", "uk")) 
    
    all <- bind_cols(.x, preds) %>%
      dplyr::select(-text, -seq)
    
    return(all)
  })

glimpse(parl_preds)
#save(parl_preds, file = "data/parl_preds.Rdata")
```

Bind columns of sentiment predictions to the parlspeech corpora

```{r}
load("data/parl_preds.Rdata")

parl_final <- parl_corpora %>% 
  bind_cols(parl_preds) %>%
  filter(nchars > 20) %>%
  filter(!chair) %>%
  filter(party %in% c("Con", "Lab", "LibDem", "UKIP", 
                      "PSOE", "PP", 
                      "CDU/CSU", "SPD", "GRUENE", "FDP", "PDS/LINKE")) %>%
  mutate(sentz = scale(sent)[,1]) %>%
  mutate(year = date %>% as_date %>% year) %>%
  mutate(month = date %>% as_date %>% month) %>% 
  ### Germany
  mutate(
    gov = case_when(
      ## DE
      year  %in% 2015:2018 & party %in% c("Con") ~ 1,
      year  %in% 2009:2015 & party == "LibDem" ~ 1,
      year  %in% 1997:2009 & party %in% "Lab" ~ 1,
      year  %in% 1990:1997 & party %in% "Con" ~ 1,
      ## ES
      year  %in% 2018:2019 & party %in% c("PSOE") ~ 1,
      year  %in% 2011:2018 & party == "PP" ~ 1,
      year  %in% 2004:2011 & party %in% "PSOE" ~ 1,
      year  %in% 1996:2004 & party %in% "PP" ~ 1,
      year  %in% 1982:1996 & party %in% "PSOE" ~ 1,
      ## UK
      year %in% c(2005:2008, 2013:2019) & party %in% c("SPD", "CDU/CSU") ~ 1,
      year == c(1994:1997,  2009:2012) & party %in% c("FDP", "CDU/CSU") ~ 1,
      year %in% 1998:2004 & party %in% c("SPD", "GRUENE") ~ 1,
      F ~ 0
    ) %>% ifelse(is.na(.), 0, .)
  )

## check the join
(parl_final$id1 == parl_final$id) %>% table

parl_final %>% glimpse
```


```{r}
parl_final %>%
  mutate(parliament = factor(parliament, levels = c("UK-HoC", "DE-Bundestag", "ES-Congresso"))) %>%
  mutate(gov = ifelse(gov == 1, "Gov", "Opp") %>% factor(., levels = c("Opp", "Gov"))) %>% 
  group_by(parliament, speaker, gov) %>%
  summarise(sentz = mean(sentz), n = n(), sent = mean(sent)) %>%
  ungroup %>% 
  filter(n > 5) %>% 
  arrange(speaker) %>% 
  group_by(speaker) %>% 
  mutate(n_speaker = n()) %>%
  ungroup %>% 
  filter(n_speaker > 1) %>%
  # group_by(parliament) %>%
  # mutate(sentzp = scale(sent)[,1]) %>%
  # ungroup %>% 
  ggplot(aes(gov, sentz, fill = gov)) +
  geom_violin(alpha = .4, color = NA) +
  geom_line(aes(group = speaker), alpha = .2, color = "gray50", size = .3) +
  labs(x = "", y = "Standardized Sentiment") + 
  scale_fill_manual("", values = c("red", "blue")) +
  facet_wrap(~parliament) +
  theme(legend.position = "none")
```


```{r}
sent_compare_de <- parl_final %>% 
  filter(nchars > 20) %>%
  filter(!chair) %>%
  filter(parliament == "DE-Bundestag") %>%
  filter(party != "independent") %>%
  mutate(sentz = scale(sent)[,1]) %>%
  mutate(year = date %>% as_date %>% year) %>%
  mutate(month = date %>% as_date %>% month) %>% 
  group_by(parliament, year, party, gov) %>%
  summarise(msent = mean(sentz, na.rm = T), n = n()) %>% 
  ungroup 

sent_compare_de  %>%
  ggplot(aes(year, msent, colour = party)) +
  geom_line() + 
  facet_wrap(~party) +
  scale_fill_manual(values = c("white", "gray50")) +
  scale_colour_manual(values = party_colors) +
  theme(legend.position = "bottom") +
  guides(color = F) +
  add_election(sent_compare_de)
```


```{r}
sent_compare_uk <- parl_final %>%
  filter(nchars > 20) %>%
  filter(!chair) %>%
  filter(parliament == "UK-HoC") %>%
  filter(party %in% c("Con", "Lab", "LibDem", "UKIP")) %>%
  mutate(party = as.character(party)) %>%
  mutate(sentz = scale(sent)[,1]) %>%
  mutate(year = date %>% as_date %>% year) %>%
  mutate(month = date %>% as_date %>% month) %>% 
  group_by(parliament, year, party, gov) %>%
  summarise(msent = mean(sentz, na.rm = T), n = n()) %>% 
  ungroup

sent_compare_uk  %>%
  ggplot(aes(year, msent, colour = party)) +
  geom_line() + 
  facet_wrap(~party) +
  scale_fill_manual(values = c("white", "gray50")) +
  theme(legend.position = "bottom") +
  guides(color = F) +
  add_election(sent_compare_uk)
```


```{r}
sent_compare_es <- parl_final %>% 
  filter(nchars > 20) %>%
  filter(!chair) %>%
  filter(parliament == "ES-Congresso") %>%
  filter(party %in% c("PSOE", "PP")) %>% # , "IU", "CiU"
  mutate(sentz = scale(sent)[,1]) %>%
  mutate(year = date %>% as_date %>% year) %>%
  mutate(month = date %>% as_date %>% month) %>% 
  group_by(parliament, year, party, gov) %>%
  summarise(msent = mean(sentz, na.rm = T), n = n()) %>% 
  ungroup

sent_compare_es  %>%
  ggplot(aes(year, msent, colour = party)) +
  geom_line() + 
  facet_wrap(~party, ncol = 1) +
  scale_fill_manual(values = c("white", "gray50")) +
  add_election(sent_compare_es)
```


# Session

```{r}
sessionInfo()
```